Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2023-07-14 ms_draft07.06.Rmd

---
title: "Grip strength, mating success, and immune function in US adults: a registered report "
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(ggplot2)
library(dplyr)
library(psych)
library(xtable)
library(knitr)
library(kableExtra)
library(weights)
library(jtools)
library(reshape2)
library(gtsummary)
library(corrplot)
source('draft_analysis.R')
```
EHB Registered Report

@@

In humans, the immunocompetence hypothesis has primarily been leveraged to explain male facial masculinity and voice pitch but it and more general cost models have also been argued to explain apparent female preference for muscular male body types (Boothroyd et al., 2013).

@@

#### 2.1.2 Key predictor variables: 
Our main predictor variable is formidability, which Lassek and Gaulin operationalized as fat-free mass and limb muscle volume. Since those variables were not available in our data, we operationalized formidability as combined grip strength (kg), the sum of the highest of three readings taken on each hand using a dynamometer. All regression models also included sex (male/female), age in years, and partnered status (not included in models where partnered status was the outcome variable). The interaction between sex and strength was crucial for our models since we want to test if the effect of strength on mating and immune outcomes is different for women than for men. Likewise, we also interacted age and partnered status with sex. We interacted age with sex since menopause occurs within the age range of our participants. For models of past year number of sexual partners we included an interaction between partnered status and grip strength since being currently partnered would plausibly impact mating behavior in the past year regardless of strength. Continuous-valued predictor variables were centered and standardized by 2 standard deviations which approximately matches the variation in binary variables like sex, thus making the regression coefficients more comparable (Gelman, CITE).

@@

#### Socioeconomic control model
The socioeconomic control model included education and race as categorical variables, since there is evidence that race is related to variation in both strength (Johnson & Wilson, 2019) and sexual behavior (Fenton et al., 2005). Likewise, there is also variation in sexual behavior by education (Chandra et al., 2011). physical fitness (CITE).

#### Health control model
An umbrella review found the grip strength is a useful indicator of general health status, early all-cause mortality, cardiovascular mortality, and disability (Soysal et al., 2021). Furthermore, health status is associated with higher likelihood of sexual activity, frequency of sexual activity, and reported quality of sex in men and women (Lindau et al., 2009). Another study of men aged 45-59 found that lower sexual activity was associated with increased mortality (Smith et al., 1997). The health model, therefore, included a number of variables related to health. White blood cell count (1000 cells/ µL) and hemoglobin (g/dL) were included to control for acute infection. Depression, which is negatively related to strength (Smith et al., 2022), was measured using the Patient Health Questionnaire-9 (PHQ-9), a validated nine-item screening instrument. Each item represents a symptom of depression, and for each one participants were asked to consider how frequently they had been bothered by that symptom over the past two weeks, rated on a scale from 0 (not at all) to 3 (nearly everyday). These ratings were summed to produce a depression score ranging from 0-27. Chronic illness was included using Chronic Disease Score (0-6) a count of chronic diseases participants reported having been diagnosed with including diabetes, cancer, stroke, arthritis, heart disease and respiratory disease. A point was added for each disease a participant reported being diagnosed with, regardless of any impairment due to the disease. We then controlled for impairment resulting from chronic illness (Disease Impairment Score; 0-5) calculated from a different NHANES question, which asked participants to list up to five health conditions that specifically cause them to have difficulties with physical activities. We also controlled for physical disability and using the item "special equipment" which referred to participants' report that they needed special equipment to walk. Finally the 'perceived abnormal weight' variable was coded as true or false depending on whether a participant reported that they perceived their weight to be abnormal.

@@

#### Physical activity control model
The physical activity control model included four dichotomous variables of vigorous and moderate work and recreational activity coded as 1 if participants reported that their work and/or recreation caused large increases in heart rate or breathing for at least 10 minutes continuously (vigorous work and/or rec), or small increases in breathing or heart rate for 10 minutes continuously (moderate work and/or rec), and zero if they reported their work and/or recreation did not.

@@

Following the significant predictors reported in Lassek and Gaulin (2009, Table 4), we first specified a model with age, sex, strength, and BMI. We also included an age:sex interaction because we expected that immune investment over the lifespan might differ between males and females due to menopause in women. Finally, we included a strength:sex interaction to test the hypothesis that the immune costs of strength differ by sex.

Based on exploratory analysis we developed a second model of WBCC that included a few additional controls. First, we controlled for sex-specific testosterone and an interaction of sex and sex-specific testosterone since testosterone possibly has immunosuppressive effects, which may differ by sex (CITE). We also controlled for three variables related to energy availability that could impact immune investment: food insecurity, total MET, and average calories per day.

#### Dietary Energy Intake
Based on Lassek and Gaulin (2009, Table 3) we developed a model of dietary energy intake (average calories per day) and included age, sex, strength, BMI, and total MET. We did not include interactions with sex in this model because we do not anticipate sex differences in the effects of any predictor variable, nor did we see any in exploratory analyses.

We then developed a second model that also controlled for WBCC and food insecurity, since either could influence energy intake and strength.

### Analysis 
All analyses were completed in `r R.version.string`, using the survey package (Lumley, CITE) in order to incorporate the survey sampling weights and to preserve the representative structure of the sample. For models of lifetime and past year numbers of partners we modeled the outcomes using a poisson distribution, since these variables are count data. Models of age at first sexual intercourse and white blood cell count utilized a normal distribution. Analyses include adults ages 18-59 because this is the period when the majority of reproduction takes place and because these are the years when grip strength is the most stable.

@@

@@

getn <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(age,
                height,
                weight,
                bmi,
                strength,
                whitebloodcell,
                hemoglobin,
                testosterone),
    statistic = list(
      all_continuous() ~ "{N_nonmiss_unweighted}"
    ),
    digits = all_continuous() ~ 0,
    missing = "no"
  )

getratio <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(age,
                height,
                weight,
                bmi,
                strength,
                whitebloodcell,
                hemoglobin,
                testosterone),
    statistic = list(
      all_continuous() ~ "{mean}"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = round(as.numeric(stat_1)/as.numeric(stat_2), digits = 2))
  )

tab1 <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
      age,
      height,
      weight,
      bmi,
      strength,
      whitebloodcell,
      hemoglobin,
      testosterone
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = all_continuous() ~ 2,
    label  = list(
      strength = "Combined Grip Strength (kg)",
      height = "Height (cm)",
      weight = "Weight (kg)",
      age = "Age (years)",
      bmi = "Body mass index (kg/m^2^)",
      whitebloodcell = "White blood cell count (1000 cells/µL)",
      hemoglobin = "Hemoglobin (g/dL)",
      testosterone = "Testosterone (ng/dL)"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = getratio$table_body$ratio, digits = 2) %>%
      dplyr::mutate(n_male = getn$table_body$stat_1, digits = 2) %>%
      dplyr::mutate(n_female = getn$table_body$stat_2, digits = 2) %>%
      dplyr::relocate(n_male, .before = stat_1) %>%
      dplyr::relocate(n_female, .before = stat_2)
  )  %>%
  add_difference(test = everything() ~ "smd",
                 estimate_fun = purrr::partial(style_ratio, digits = 2)) %>%
  modify_column_hide(columns = ci) %>%
  modify_header(
    label = "**Variable**",
    ratio = "**Ratio**",
    n_male = "**N**",
    n_female = "**N**",
    stat_1 = "**Mean (SD)**",
    stat_2 = "**Mean (SD)**",
    estimate = "*d*"
  ) %>%
  modify_spanning_header(list(
    c("stat_1", "n_male") ~ "**Male**",
    c("stat_2", "n_female") ~ "**Female**",
    c("ratio", "estimate") ~ "**Sexual Dimorphism**"
  )) %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_caption("**Sex differences for participants ages 18-59 using population weights**") %>%
  bold_labels()

tab1

@@

```{r baseline, fig.width = 12, fig.height = 8, fig.cap = "Anthropometric Models: Coefficent plot from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standarized by 2 SD."}

forestplot(
  m_agefirst,
  m_lifetime,
  m_pastyear,
  m_partnered,
  intercept = F,
  facet = F,
  dodgewidth = .5,
  modelnames = mnames1,
  varnames = vnames
) + theme_minimal(15) +
  geom_pointrange(size = 1.2, position = position_dodge(width = .5)) +
#  labs(title = "Figure 1. Baseline Models: Regression coefficients from generalized linear models", color = "Model") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
# 
# 
# annotate_figure(fig1,
#                            top = text_grob("Figure 1. Baseline Models: Regression coefficients from generalized linear models\n",
#                                            size = 20, face = "bold",
#                                            hjust = 0,
#                                            x = 0.01),
#                            bottom = text_grob("Variables labelled (S) have been centered at the mean and standarized by 2 SD",
#                                               size = 12))

@@

@@

```{r controls, fig.width = 12, fig.height = 42, fig.cap = "Control Models: Coefficent plots from generalized linear models. Variables labelled (S) have been centered at the mean and standarized by 2 SD."}

@@

fig1 <- forestplot(
   msoc1, mheal1, mphys1, mhor1,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames, varnames = vnames) + theme_minimal() +
  theme(axis.text.y = element_text(size = 12)) +
 # geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Lifetime Number of Sexual Partners") 
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig2 <- forestplot(
 msoc2,mheal2, mphys2, mhor2,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames
) + theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(.8)) +
  labs(title = "Past Year Number of Sexual Partners")  +
  theme(axis.text.y = element_blank())
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig3 <- forestplot(
  msoc3, mheal3, mphys3, mhor3,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames) +
  theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Age at First Sex")  +
  theme(axis.text.y = element_blank())
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig4 <- forestplot(
  msoc4, mheal4, mphys4, mhor4,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames) +
  theme_minimal() + 
  #geom_pointrange(size = 1.2, position = position_dodge(width = .8)) +
  labs(title = "Currently Partnered")  +
  theme(axis.text.y = element_blank())
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

(fig1 + fig2 + fig3 + fig4) + plot_layout(guides = "collect", ncol = 4) & theme(legend.position = "bottom")

@@

@@

Previous research found that higher musculature was associated with decreased investment in native immunity. We developed two models of immune investment in white blood cell count (\@ref(fig:immune)). In the replication model, strength was a significant negative predictor of WBCC for both men and women (there was no significant interaction of sex and strength) controlling for age and BMI. In the expanded control model, this pattern remained even with additional controls (see Table ).

```{r immune, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of immune investment. Variables labelled (S) have been centered at the mean and standarized by 2 SD."}
forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  varnames = vnames) +
  theme_minimal(25) +
  geom_pointrange(size = 2, position = position_dodge(width = .8)) +
  labs(title = "White blood cell count") 
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))

@@

Finally, we tested whether strength was related to increased energy intake. We found that strength was a significant, positive predictor of energy intake controlling for sex. In the expanded control model we found the same pattern while controlling for additional variables.

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(ggplot2)
library(dplyr)
library(psych)
library(xtable)
library(knitr)
library(kableExtra)
library(weights)
library(jtools)
library(reshape2)
library(gtsummary)
library(corrplot)
library(patchwork)
source('draft_analysis.R')
```
EHB Registered Report

## Abstract

Theory and evidence suggest that the mating benefits of muscle mass in human males trade off with costs of increased energy intake and decreased measures of native immunity, likely due to an evolutionary history of sexual selection. It is unknown if females experience a similar tradeoff. Using data from the 2013-2014 phase of the National Health and Nutrition Examination Survey (NHANES), a large nationally representative sample of the US (N = 4384), we will test whether grip strength, a proxy for upper body strength and physical formidability, is a positive predictor of self-reported measures of adult mating success (lifetime number of sexual partners, past year number of sexual partners, age at first intercourse, and current partnership status) in both males and females, controlling for numerous anthropometric, socioeconomic, hormone, health, and physical activity related potential confounds. We will also test if there is a positive relationship between grip strength and dietary energy intake, and a negative relationship between grip strength and native immune function. This study replicates an earlier study of US males (Lassek & Gaulin, 2009) and additionally tests these relationships in females.

@@

In humans, the immunocompetence hypothesis has primarily been leveraged to explain male facial masculinity and voice pitch but it and more general cost models have also been argued to explain apparent female preference for muscular male body types (Frederick & Haselton, 2007). Cues of upper body strength indeed account for most of the variation in female-rated male body attractiveness (Sell et al., 2017).

@@

#### 2.1.2 Key predictor variables: 
Our main predictor variable is formidability, which Lassek and Gaulin operationalized as fat-free mass and limb muscle volume. Since those variables were not available in our data, we operationalized formidability as combined grip strength (kg), the sum of the highest of three readings taken on each hand using a dynamometer. All regression models also included sex (male/female), age in years, and partnered status (not included in models where partnered status was the outcome variable). The interaction between sex and strength was crucial for our models since we want to test if the effect of strength on mating and immune outcomes is different for women than for men. Likewise, we also interacted age and partnered status with sex. We interacted age with sex since menopause occurs within the age range of our participants. For models of past year number of sexual partners we included an interaction between partnered status and grip strength since being currently partnered would plausibly impact mating behavior in the past year regardless of strength. Continuous-valued predictor variables were centered and standardized by 2 standard deviations which approximately matches the variation in binary variables like sex, thus making the regression coefficients more comparable (Gelman, 2008).

@@

#### Socioeconomic control model
The socioeconomic control model included education and race as categorical variables, since there is evidence that race is related to variation in both strength (Johnson & Wilson, 2019) and sexual behavior (Fenton et al., 2005). Likewise, there is also variation in sexual behavior by education (Chandra et al., 2013), likewise there is variation in physical activity by education (He & Baker, 2005).

#### Health control model
An umbrella review found the grip strength is a useful indicator of general health status, early all-cause mortality, cardiovascular mortality, and disability (Soysal et al., 2021). Furthermore, health status is associated with higher likelihood of sexual activity, frequency of sexual activity, and reported quality of sex in men and women (Lindau & Gavrilova, 2010). Another study of men aged 45-59 found that lower sexual activity was associated with increased mortality (Smith et al., 1997). The health model, therefore, included a number of variables related to health. White blood cell count (1000 cells/ µL) and hemoglobin (g/dL) were included to control for acute infection. Depression, which is negatively related to strength (Smith et al., 2022), was measured using the Patient Health Questionnaire-9 (PHQ-9; Kroenke et al., 2001), a validated nine-item screening instrument. Each item represents a symptom of depression, and for each one participants were asked to consider how frequently they had been bothered by that symptom over the past two weeks, rated on a scale from 0 (not at all) to 3 (nearly everyday). These ratings were summed to produce a depression score ranging from 0-27. Chronic illness was included using Chronic Disease Score (0-6) a count of chronic diseases participants reported having been diagnosed with including diabetes, cancer, stroke, arthritis, heart disease and respiratory disease. A point was added for each disease a participant reported being diagnosed with, regardless of any impairment due to the disease. We then controlled for impairment resulting from chronic illness (Disease Impairment Score; 0-5) calculated from a different NHANES question, which asked participants to list up to five health conditions that specifically cause them to have difficulties with physical activities. We also controlled for physical disability and using the item "special equipment" which referred to participants' report that they needed special equipment to walk. Finally the 'perceived abnormal weight' variable was coded as true or false depending on whether a participant reported that they perceived their weight to be abnormal.

@@

#### Physical activity control model
Physical activity is related to sexual behavior and function in adults (Morris et al., 2022). Therefore, the physical activity control model included four dichotomous variables of vigorous and moderate work and recreational activity coded as 1 if participants reported that their work and/or recreation caused large increases in heart rate or breathing for at least 10 minutes continuously (vigorous work and/or rec), or small increases in breathing or heart rate for 10 minutes continuously (moderate work and/or rec), and zero if they reported their work and/or recreation did not.

@@

Following the significant predictors reported in Lassek and Gaulin (2009, Table 4), we first specified a replication model with age, sex, strength, and BMI. We also included an age:sex interaction because we expected that immune investment over the lifespan might differ between males and females due to menopause in women. Finally, we included a strength:sex interaction to test the hypothesis that the immune costs of strength differ by sex.

Based on exploratory analysis we developed an expanded control model of WBCC that included a few additional controls. First, we controlled for sex-specific testosterone and an interaction of sex and sex-specific testosterone since testosterone possibly has immunosuppressive effects, which may differ by sex. We also controlled for three variables related to energy availability that could impact immune investment. First, food security status for adults in the participant's household was assessed using 10 items from the U.S. Food Security Survey Module. The resulting value can range from 1-4, where 1 represents full food security and 4 represents very low food security. Second, the total metabolic equivalent (total MET) was calculated based on participants' responses to questions about the minutes they spent walking or bicycling, engaging in vigorous and moderate work, and vigorous and moderate recreation per day, using MET scores provided by NHANES.  Finally we included dietary energy intake (average calories per day as discussed above).

#### Dietary Energy Intake
Based on Lassek and Gaulin (2009, Table 3) we developed a replication model of dietary energy intake (average calories per day) and included age, sex, strength, BMI, and total MET. We did not include interactions with sex in this model because we do not anticipate sex differences in the effects of any predictor variable, nor did we see any in exploratory analyses.

We then developed an expanded control model that also controlled for WBCC and food insecurity in addition to the variables in the model above, since either could influence energy intake and strength.

### Analysis 
All analyses were completed in `r R.version.string`, using the survey package (version 4.1-1; Lumley, 2021) in order to incorporate the survey sampling weights and to preserve the representative structure of the sample. For models of lifetime and past year numbers of partners we modeled the outcomes using a poisson distribution, since these variables are count data. Models of age at first sexual intercourse and white blood cell count utilized a normal distribution. Analyses include adults ages 18-60 because this is the period when the majority of reproduction takes place and because these are the years when grip strength is the most stable.

@@

```{r sexual dimorphism}
getncat <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
                partnered,
                edu,
                race,
                perceived_abnormal_weight,
                special_equipment,
                vigorous_work,
                moderate_work,
                vigorous_rec,
                moderate_rec),
    statistic = list(
      all_categorical() ~ "{N_nonmiss_unweighted}"
    ) , missing = "no" )

cat <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
      partnered,
      edu,
      race,
      perceived_abnormal_weight,
      special_equipment,
      vigorous_work,
      moderate_work,
      vigorous_rec,
      moderate_rec
    ),
    label  = list(
      partnered = "Partnered",
      edu = "Education",
      race = "Race and Ethnicity",
      perceived_abnormal_weight = "Perceived abnormal weight",
      special_equipment = "Special equipment needed to walk",
      vigorous_work = "Work involves vigorous activity",
      moderate_work = "Work involves moderate activity",
      vigorous_rec = "Recreation involves vigorous activity",
      moderate_rec = "Recreation involves moderate activity"
    ),
    statistic = list(all_categorical() ~ "{n_unweighted} ({p}%)"),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(n_male = getncat$table_body$stat_1, digits = 2) %>%
      dplyr::mutate(n_female = getncat$table_body$stat_2, digits = 2) %>%
      dplyr::relocate(n_male, .before = stat_1) %>%
      dplyr::relocate(n_female, .before = stat_2)
  ) %>% 
  modify_header(
    label = "**Variable**",
    n_male = "**N**",
    n_female = "**N**",
    stat_1 = "**Mean (SD) or n (%)**",
    stat_2 = "**Mean (SD) or n (%)**",
  ) %>%
  modify_spanning_header(list(
    c("stat_1", "n_male") ~ "**Male**",
    c("stat_2", "n_female") ~ "**Female**"
  )) %>% 
  bold_labels()

#####

getncon <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(age_first_sex,
                sex_partners,
                sex_partners_year,
                strength,
                age,
                bmi,
                height,
                weight,
                whitebloodcell,
                hemoglobin,
                testosterone, 
                chronic_disease_score,
                physical_disease_count,
                depression,
                avgcalories, 
                foodinsecurity_adult, 
                tot_MET),
    statistic = list(
      all_continuous() ~ "{N_nonmiss_unweighted}",
      all_categorical() ~ "{N_nonmiss_unweighted}"
    ),
    digits = all_continuous() ~ 0,
    type = list(
      chronic_disease_score ~ "continuous",
      physical_disease_count ~ "continuous", 
      foodinsecurity_adult ~ "continuous"
    ),
    missing = "no"
  )

getratio <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(age_first_sex,
                sex_partners,
                sex_partners_year,
                strength,
                age,
                bmi,
                height,
                weight,
                whitebloodcell,
                hemoglobin,
                testosterone, 
                chronic_disease_score,
                physical_disease_count,
                depression,
                avgcalories, 
                foodinsecurity_adult, 
                tot_MET),
    statistic = list(
      all_continuous() ~ "{mean}",
      all_categorical() ~ "{p}"
    ),
    digits = list(
      all_continuous() ~ c(2)
                  ), 
    type = list(
      chronic_disease_score ~ "continuous",
      physical_disease_count ~ "continuous",
      foodinsecurity_adult ~ "continuous"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = round(as.numeric(stat_1)/as.numeric(stat_2), digits = 2))
  )

con <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
      age_first_sex,
      sex_partners,
      sex_partners_year,
      strength,
      age,
      bmi,
      height,
      weight,
      whitebloodcell,
      hemoglobin,
      testosterone, 
      chronic_disease_score,
      physical_disease_count,
      depression,
      avgcalories, 
      foodinsecurity_adult, 
      tot_MET
    ),
    label  = list(
      age_first_sex = "Age at first sex (years)",
      sex_partners = "Lifetime number of sexual partners",
      sex_partners_year = "Past year number of sexual partners",
      strength = "Combined Grip Strength (kg)",
      age = "Age (Years)",
      bmi = "Body mass index (kg/m^2)",
      height = "Height (cm)",
      weight = "Weight (kg)",
      whitebloodcell = "White blood cell count (1000 cells/µL)",
      hemoglobin = "Hemoglobin (g/dL)",
      testosterone = "Testosterone (ng/dL)",
      chronic_disease_score = "Chronic Disease Score (0-6)",
      physical_disease_count = "Disease Impairment Score (0-5)",
      depression = "Depression Score (0-27)",
      avgcalories = "Dietary energy intake (kcals)", 
      foodinsecurity_adult = "Food Insecurity Rating (1-4)", 
      tot_MET = "Total MET"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n_unweighted} ({p}%)"),
    digits = all_continuous() ~ 2,
    type = list(
      chronic_disease_score ~ "continuous",
      physical_disease_count ~ "continuous", 
      foodinsecurity_adult ~ "continuous"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = getratio$table_body$ratio, digits = 2) %>%
      dplyr::mutate(n_male = getncon$table_body$stat_1, digits = 2) %>%
      dplyr::mutate(n_female = getncon$table_body$stat_2, digits = 2) %>%
      dplyr::relocate(n_male, .before = stat_1) %>%
      dplyr::relocate(n_female, .before = stat_2)
  )  %>%
  add_difference(test = everything() ~ "smd",
                 estimate_fun = purrr::partial(style_ratio, digits = 2)) %>%
  modify_column_hide(columns = ci) %>%
  modify_header(
    label = "**Variable**",
    ratio = "**Ratio**",
    n_male = "**N**",
    n_female = "**N**",
    stat_1 = "**Mean (SD)**",
    stat_2 = "**Mean (SD)**",
    estimate = "*d*"
  ) %>%
  modify_spanning_header(list(
    c("stat_1", "n_male") ~ "**Male**",
    c("stat_2", "n_female") ~ "**Female**",
    c("ratio", "estimate") ~ "**Sexual Dimorphism**"
  )) %>%
  modify_footnote(all_stat_cols() ~ "Weighted means and standard deviations shown for continuous variables, unweighted n (%) for categorical variables") %>%
  modify_caption("**Sex differences for participants ages 18-60 using population weights**") %>%
  bold_labels()

tbl_stack(list(con, cat))
```

@@

# getn <- designsG$d.design.adults %>%
#   tbl_svysummary(
#     by = sex,
#     include = c(age,
#                 height,
#                 weight,
#                 bmi,
#                 strength,
#                 whitebloodcell,
#                 hemoglobin,
#                 testosterone),
#     statistic = list(
#       all_continuous() ~ "{N_nonmiss_unweighted}"
#     ),
#     digits = all_continuous() ~ 0,
#     missing = "no"
#   )
# 
# getratio <- designsG$d.design.adults %>%
#   tbl_svysummary(
#     by = sex,
#     include = c(age,
#                 height,
#                 weight,
#                 bmi,
#                 strength,
#                 whitebloodcell,
#                 hemoglobin,
#                 testosterone),
#     statistic = list(
#       all_continuous() ~ "{mean}"
#     ),
#     missing = "no"
#   ) %>%
#   modify_table_body(
#     ~ .x %>%
#       dplyr::mutate(ratio = round(as.numeric(stat_1)/as.numeric(stat_2), digits = 2))
#   )
# 
# 
# 
# tab1 <- designsG$d.design.adults %>%
#   tbl_svysummary(
#     by = sex,
#     include = c(
#       age,
#       height,
#       weight,
#       bmi,
#       strength,
#       whitebloodcell,
#       hemoglobin,
#       testosterone
#     ),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     digits = all_continuous() ~ 2,
#     label  = list(
#       strength = "Combined Grip Strength (kg)",
#       height = "Height (cm)",
#       weight = "Weight (kg)",
#       age = "Age (years)",
#       bmi = "Body mass index (kg/m^2^)",
#       whitebloodcell = "White blood cell count (1000 cells/µL)",
#       hemoglobin = "Hemoglobin (g/dL)",
#       testosterone = "Testosterone (ng/dL)"
#     ),
#     missing = "no"
#   ) %>%
#   modify_table_body(
#     ~ .x %>%
#       dplyr::mutate(ratio = getratio$table_body$ratio, digits = 2) %>%
#       dplyr::mutate(n_male = getn$table_body$stat_1, digits = 2) %>%
#       dplyr::mutate(n_female = getn$table_body$stat_2, digits = 2) %>%
#       dplyr::relocate(n_male, .before = stat_1) %>%
#       dplyr::relocate(n_female, .before = stat_2)
#   )  %>%
#   add_difference(test = everything() ~ "smd",
#                  estimate_fun = purrr::partial(style_ratio, digits = 2)) %>%
#   modify_column_hide(columns = ci) %>%
#   modify_header(
#     label = "**Variable**",
#     ratio = "**Ratio**",
#     n_male = "**N**",
#     n_female = "**N**",
#     stat_1 = "**Mean (SD)**",
#     stat_2 = "**Mean (SD)**",
#     estimate = "*d*"
#   ) %>%
#   modify_spanning_header(list(
#     c("stat_1", "n_male") ~ "**Male**",
#     c("stat_2", "n_female") ~ "**Female**",
#     c("ratio", "estimate") ~ "**Sexual Dimorphism**"
#   )) %>%
#   modify_footnote(update = everything() ~ NA) %>%
#   modify_caption("**Sex differences for participants ages 18-59 using population weights**") %>%
#   bold_labels()
# 
# tab1

@@

```{r baseline, fig.width = 12, fig.height = 8, fig.cap = "Anthropometric models of mating success (Pilot): Coefficient plot from generalized linear models. Variables labelled (S) have been centered at the mean and standardized by 2 SD."}

Figure1 <- forestplot(
  m_agefirst,
  m_lifetime,
  m_pastyear,
  m_partnered,
  intercept = F,
  facet = F,
  dodgewidth = .5,
  modelnames = mnames1,
  varnames = vnames, 
  size = 1.2, 
  linewidth = 1
) + theme_minimal(17) +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .5)) +
#  labs(title = "Figure 1. Baseline Models: Regression coefficients from generalized linear models", color = "Model") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
# 
# 
# annotate_figure(fig1,
#                            top = text_grob("Figure 1. Baseline Models: Regression coefficients from generalized linear models\n",
#                                            size = 20, face = "bold",
#                                            hjust = 0,
#                                            x = 0.01),
#                            bottom = text_grob("Variables labelled (S) have been centered at the mean and standarized by 2 SD",
#                                               size = 12))

@@

ggsave("Figures/Figure1.pdf", Figure1, width = 14, height = 7)

Figure1
```

@@

```{r controls, fig.width = 12, fig.height = 42, fig.cap = "Additional control models (Pilot): Coefficient plots for predictors of mating success from generalized linear models. Variables labelled (S) have been centered at the mean and standardized by 2 SD."}

@@

fig1 <- forestplot(
   msoc1, mheal1, mphys1, mhor1,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames, 
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) + theme_minimal() +
  theme(axis.text.y = element_text(size = 9), plot.title = element_text(size = 11)) +
 # geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Lifetime Number of Sexual Partners") 
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig2 <- forestplot(
 msoc2,mheal2, mphys2, mhor2,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
 size = 0.7, 
  linewidth = 0.7
) + theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(.8)) +
  labs(title = "Past Year Number of Sexual Partners")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig3 <- forestplot(
  msoc3, mheal3, mphys3, mhor3,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) +
  theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Age at First Sex")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig4 <- forestplot(
  msoc4, mheal4, mphys4, mhor4,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) +
  theme_minimal() + 
  #geom_pointrange(size = 1.2, position = position_dodge(width = .8)) +
  labs(title = "Currently Partnered")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

Figure2 <- (fig1 + fig2 + fig3 + fig4) + plot_layout(guides = "collect", ncol = 4) & theme(legend.position = "bottom")

@@

ggsave("Figures/Figure2.pdf", Figure2, width = 14, height = 7)

Figure2

@@

Previous research found that higher musculature was associated with decreased investment in native immunity. We developed two models of immune investment in white blood cell count (Figure \@ref(fig:immune)). In the replication model, strength was a significant negative predictor of WBCC for both men and women (there was no significant interaction of sex and strength) controlling for age and BMI. In the expanded control model, this pattern remained even with additional controls (see Table ).

```{r immune, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of predictors of immune investment (WBCC) from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standardized by 2 SD."}
Figure3 <- forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  theme_minimal(17) +
 # geom_pointrange(size = 2, position = position_dodge(width = .8)) +
 # labs(title = "White blood cell count") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))

ggsave("Figures/Figure3.pdf", Figure3, width = 14, height = 7)

Figure3

@@

Finally, we tested whether strength was related to increased energy intake (Figure \@ref(fig:dietary)). We found that strength was a significant, positive predictor of energy intake controlling for sex. In the expanded control model we found the same pattern while controlling for additional variables.
